---
title: "Basic shortwave model exploration"
output:
  html_notebook: default
  html_document:
    df_print: paged
  pdf_document: default
editor_options: 
  markdown: 
    wrap: 72
---
# Model exploration

this is a testing notebook where the various model componets are tested and explored
### Import the shortwave model code

```{r}
source("../radiative_transfer_model/shortwave.R")
source("../radiative_transfer_model/longwave.R")
source("../radiative_transfer_model/calc_parameters.R")
library(tidyverse)
library(readxl)
```

### Define the parameters

```{r}
params <- list(
  rho_leaf = 0.057,                   # Leaf reflectance
  tau_leaf = 0.048,                   # Leaf transmittance
  Kb = 0.58,                          # Direct beam extinction coefficient
  Kd = 0.70,                          # Diffuse extinction coefficient
  beta = 0.54,                        # Upscatter parameter for diffuse radiation
  beta0 = 0.46,                       # Upscatter parameter for direct beam radiation
  clump_OMEGA = 0.75,                 # Clumping coefficient 
  alb_soil_b = 0.1,                   # Soil albedo (direct)  
  alb_soil_d = 0.1,                   # Soil albedo (diffuse)
  em_leaf = .97,                      # Emissivity leaves
  em_soil = 1.00,                     # Emissivity soil
  sigma = 5.67e-08,                   # Stefan-Boltzmann constant (TODO: Unit)
  
  lat = 51.099,                       # Latitude for Hainich 
  lon = 10.426,                       # Longitude for Hainich
  leaf_out = 110,                     # start of leaf out
  leaf_full = 170,                    # day of full leaves
  leaf_fall = 280,                    # day of leaf fall
  leaf_fall_complete = 300,           # day of leaf fall end
  max_LAI = 5                         # Max LAI in summer
)

params$omega_leaf = params$rho_leaf + params$tau_leaf   # Leaf scattering coefficient
```

### Define the inputs

```{r}
inputs <- list(
  sw_sky_b = 0.8,             # Short wave (sw) direct beam radiation (W m^-2)
  sw_sky_d = 0.2,             # Short wave (sw) diffuse radiation (W m^-2)
  lw_sky = 400,               # Long wave (sw) diffuse radiation (W m^-2)
  t_leaf = 273.15 + 25,
  t_soil =273.15 + 20,
  LAI = 6                    # Leaf Area Index
)

```

Read the flux data from the excel file
```{r}
flux <- read_excel("../../data/FLX_DE-Hai_FLUXNET2015_FULLSET_HH_2016-2018_beta-3_for_class.xlsx", na = "-9999.000") %>%
    select("Date/Time", SW_IN_F, SW_DIF, SW_OUT, LW_IN_F, LW_OUT) %>%
    rename(time = "Date/Time")
```

test run of the model with the flux data
```{r}
for (i in 1:1){
  inputs <- list(
      sw_sky_b = flux[i,]$SW_IN_F,
      sw_sky_d = flux[i,]$SW_DIF,
      lw_sky = flux[i,]$LW_IN_F,
      t_leaf = 273.15 + 25,
      t_soil =273.15 + 20,
      LAI = day_LAI(flux[i,]$time, params)
  )
  print(inputs)
  print(shortwave_radiation(inputs, params))
  print(longwave_radiation(inputs, params))

}
```
```{r}
flux[]
```


```{r}
flux[2,]
```

# Testing th model
### Run the model for the whole shortwave

```{r}
  shortwave_radiation(inputs, params)
```

### Longwave

```{r}
  longwave_radiation(inputs, params)
```

#### Model for direct radiation

```{r}
direct_beam_radiation(inputs, params)
```

#### Model for diffuse radiation

```{r}
diffuse_radiation(inputs, params)
```

### variation of Ic with different LAI

```{r}
out <- matrix(ncol=4, nrow=15)
for (lai in 1:15){
  inputs$LAI = lai
  ic = shortwave_radiation(inputs, params)
  out[lai,] = c(lai, ic$ic, ic$ic_sun, ic$ic_sha)
}
out <- data.frame(out)
colnames(out) <- c("LAI", "Ic", "Ic_sun", "Ic_sha")

out %>% tidyr::gather("Radiation_type", "Absorbed_radiation", 2:4) %>%
  ggplot()+
  geom_line(aes(x=LAI, y=Absorbed_radiation, color=Radiation_type))

```
```{r}
source("../radiative_transfer_model/calc_parameters.R")
```
```{r}
(Z <- get_zenith(Sys.time(), params))
```
```{r}
(LAI <- get_day_LAI(Sys.time(), params))
```
```{r}
get_Kb(Z)
curve(Vectorize(get_Kb)(x), from = 0, to = 89, xlab='Zenith', ylab = 'Kb')
```

```{r}
curve(Vectorize(get_Kd)(x), from = 1, to = 12, xlab='LAI', ylab = 'Kd')
```


