---
title: "Figures for radiative transfer model"
author: Simone Massaro
date: 19/01/21
output: pdf_document
fig.width: 11
fig.height: 7
sansfont: Calibri Light
---

```{r setup}
knitr::opts_knit$set(root.dir = '/home/simone/Documents/uni/ecosystem and atmosphere/radiative-transfer-model')
```

# Load the model and setup

```{r, results='hide', message = FALSE}
library(readxl)
library(tidyverse)
source("radiative_transfer_model.R")
```

parameters for Hainich (use as default parameters for model)
```{r, results='hide', message = FALSE}
source('parameters_hainich.R')
p <-  params
```

## LAI over the year
See how the LAI changes over the year
```{r}
days <- seq.Date(as.Date("2020-01-01"), as.Date("2020-12-31"), by=1)
LAIs <- Vectorize(get_day_LAI, "datetime")(days,  p$max_LAI, p$min_LAI, p$leaf_out, p$leaf_full, p$leaf_fall, p$leaf_fall_complete)

ggplot() + geom_line(aes(x=days, y=LAIs))
```
# Test with sample
In this section we create some sample in put and we change only one variable to see how the model output respond to this

## Absorbed radiation vs LAI

The increase in LAI increase the amount of radiation absorbed, but then it reaches a peak at even if the LAI increase no more light is absorbed.
```{r}

fake_input_2 <- tibble(
    datetime = as.Date("2020-07-15 12:00"), # Summer day
    sw_sky_b = 900,
    sw_sky_d = 100,
    lw_sky = 200,
    t_soil = 300,
    t_leaf = 300,
    LAI = 1:10,
    zenith = 30,
)
out_2 <- radiative_transfer_over_input(fake_input_2, p)

out_2 %>%
        gather("Radiation_type", "Absorbed_radiation", c("ic", "ic_sun", "ic_sha")) %>%
        ggplot() +
        geom_line(aes(x=LAI, y=Absorbed_radiation, color=Radiation_type, linetype=Radiation_type))
```
Variation of absorbed radiation by the soil and canopy with the variation of LAI

We can see that the overall canopy albedo is constant while the division between soil and canopy changes
```{r}
out_2 %>%
        gather("Radiation_type", "Radiation", c("ic", "ig", "i_up")) %>%
        ggplot() +
        geom_line(aes(x=LAI, y=Radiation, color=Radiation_type, linetype=Radiation_type))
```

## Emitted and Absbed longwave radiation at different temperature

Soil and leaves temperature changes together between 260 and 310 K

```{r}
fake_input_3 <- tibble(
    datetime = as.Date("2020-07-15 12:00"), # Summer day
    sw_sky_b = 800,
    sw_sky_d = 100,
    lw_sky = 200,
    t_soil = 260:310,
    t_leaf = 260:310,
    zenith = 30,
)
out_3 <- radiative_transfer_over_input(fake_input_3, p)

out_3 %>% cbind(select(fake_input_3, -zenith)) %>%
        gather("Radiation_type", "Radiation", c("lc", "l_up")) %>%
        ggplot() +
        geom_line(aes(x=t_leaf, y=Radiation, color=Radiation_type))
```


## Absorbed radiation vs zenith

Variation of the fraction of soil radiation that is absorbed with the change of the solar zenith (angle between vertical and sun)

```{r}
fake_input_4 <- tibble(
    datetime = as.POSIXct("2016-07-21 00:00"), # Summer day
    zenith= seq(0,90,5),
    sw_sky_b = 800,
    sw_sky_d = 100,
    lw_sky = 200,
    t_soil = 300,
    t_leaf = 300,
)
out_4 <- radiative_transfer_over_input(fake_input_4, p)

out_4 %>%
        select(-zenith) %>%
        cbind(fake_input_4) %>%
        mutate(absorbed_fraction = ic / (sw_sky_b + sw_sky_d)) %>%
        ggplot() +
        geom_line(aes(x=zenith, y=absorbed_fraction, color="red"))
```


# Test with real data

## Load data

```{r}
source("read_data_hainich.R")
flux <-  read_fluxnet_zenith("data/fluxnet_hainich_with_zenith.csv")
```


Taking the first year of flux data
```{r}
t_data <- na.omit(flux[flux$datetime < as.Date("2016-12-30"), ])
```

## Running the model
```{r}
out <- radiative_transfer_over_input(t_data, p)
```
### Shortwave
```{r}
ggplot() +
        geom_point(aes(x=out$i_up, y=t_data$sw_out)) +
        geom_smooth(aes(x=out$i_up, y=t_data$sw_out), method='lm') +
        geom_abline(intercept = 0, slope = 1, color="red")
```

### Longwave
```{r}
ggplot() + geom_point(aes(x=out$l_up, y=t_data$lw_out)) + geom_abline(intercept = 0, slope = 1, color="red")
```

### Plot time series of some Summer days


```{r}
out %>% cbind(select(t_data, -zenith)) %>%
        filter(datetime > as.Date("2016-06-18")  & datetime < as.Date("2016-06-21")) %>%
        gather("Radiation_type", "Radiation", c("sw_out", "i_up")) %>%
        ggplot() +
        geom_line(aes(x=datetime, y=Radiation, color=Radiation_type)) +
        scale_color_hue(labels=c("Modelled upward radiation", "Measured upward radiation"))
```


